---
title: "Investigation of the double-negative/atypical memory b-cell subtype in pre- and post-menopausal breast cancer samples"
author: "Sean O'Toole"
date: "`r Sys.Date()`"
output: 
  prettydoc::html_pretty:
    theme: cayman
    toc: true
params:
  run_python_script: TRUE  # determines if the python pipeline will run, or if the script relies on already stored objects
---

# Introduction

This report investigates B-cell subtypes within pre- and post-menopausal Visium spatial transcriptomics samples. The research focuses on whether double-negative B-cell subtypes—also known as atypical memory cells or age-associated B-cells—could explain differences in patient outcomes and tumor composition between these groups.

Pre-menopausal patients often present with more aggressive tumors and more severe diagnoses compared to their post-menopausal counterparts. This analysis explores how variations in B-cell subtypes may contribute to these differences. The report details the approaches taken and the conclusions drawn from this investigation.

```{r, echo=FALSE, message=FALSE, warning=FALSE, results = 'hide', fig.show = 'hide'}
library(Seurat)
library(reticulate)

# Conditionally source the Python script
if (params$run_python_script) {
  # Run Python script using reticulate
  py_run_file('visiumPythonPipeline.py')
}

```

# Initialization of the data pipeline in python and R

# Subsetting based on the input from the pathologists

```{r include-png, echo=FALSE}
example_segmentation_path_pre1 <- paste0(getwd(), '/figures/PRE-01_segmentation_plots.png')
knitr::include_graphics(example_segmentation_path_pre1)
```

And as you can see blah blah blah

Below is a summary of the `cars` dataset and a corresponding scatter plot:

```{r}
# Summary of the dataset
summary(cars)

# Scatter plot of the dataset
plot(cars, main = "Scatter Plot of Cars Dataset", xlab = "Speed", ylab = "Stopping Distance", col = "blue", pch = 19)
